\documentclass[11pt,oneside,letterpaper]{article}

\usepackage{hyperref}
\usepackage{listings}
\usepackage{graphicx}

\begin{document}

\title{
    Role-Based Access Control Filesystem\\
    (RBACFS) \\
    Sample Assignment
}
\author{
    Scott Linder\\
    \and
    Ryan DePrekel\\
    \and
    Justin Lanyon
}
\date{\today}

\maketitle

\begin{abstract}
UNIX permission bits do not provide fine-grained and flexible control over
access, only permitting read (r), write (w), and execute (x), permissions to be
set for user (u), group (g), and other(o). Role Based Access Control (RBAC)
allows for many roles to have different access to the same object, as opposed
to permission bits which allow at most one group and one user to have
permissions. You will implement an RBAC policy via a definitions file for
a filesystem implementing RBAC (RBACFS).
\end{abstract}

\section{Overview}

You have been given a {\tt Vagrantfile} which will create a new virtualbox
VM and automatically install RBACFS. From within the VM, change to the
{\tt /vagrant} directory, and mount the filesystem with the following line:
\begin{lstlisting}
sudo rbacfs -o allow_other mount root student.defs
\end{lstlisting}

Test the policy implementation using the following script, which will
print nothing when the solution is acceptable:
\begin{lstlisting}
./test.sh
\end{lstlisting}

In order to change the policy, the filesystem must be unmounted and remounted.
The filesystem can be unmounted with the following command:
\begin{lstlisting}
sudo fusermount -u mount
\end{lstlisting}

\section{Requirements}

Modify {\tt student.defs} to implement the following policy.

\subsection{Policy}

The {\tt admin} role must be able to read and write to the printer config file,
located at {\tt /etc/lpd.conf}, while the {\tt daemon} role must only be able
to read it.

The {\tt admin} role must be able to read the system log file at {\tt
/var/syslog}, while the {\tt daemon} role must be able to write to it.

The {\tt user} role must be able to read and write the reports files
at and under the {\tt /var/reports} directory, and read and write files at and under the {\tt /home}.

\subsection{Submissions}

The only file which must be submitted is {\tt student.defs}.

\end{document}
